Self Regulation Ontology Retest Data Report

### 2017-04-28 SRO_Report.Rmd
fixed bootstrap plot colors

```{r fig.height=36}
 boot_df %>%
  mutate(task = ifelse(grepl("survey",dv), "survey","task")) %>%
  ggplot(aes(reorder(dv, icc, FUN=var), icc, fill = task))+
  geom_boxplot()+
  geom_point(data = rel_df, aes(x=dv, y = icc, color = "yellow"))+
  theme_bw()+
  coord_flip()
```

>>>>

```{r fig.height=36}
 boot_df %>%
  mutate(task = ifelse(grepl("survey",dv), "survey","task")) %>%
  ggplot(aes(reorder(dv, icc, FUN=var), icc, fill = task))+
  geom_boxplot()+
  geom_point(data = rel_df, aes(x=dv, y = icc),  color = "yellow")+
  theme_bw()+
  theme(legend.title = element_blank())+
  coord_flip()
```
